Occultation Light Curves in Reflected Light

### 2020-04-01 tex/ms.tex
frames fig

% Shorthand for this paper
\usepackage{xifthen}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\STARRYQUADPOINTS}{100\xspace}
\newcommand{\bkappa}{\boldsymbol{\kappa}}
\newcommand{\blambda}{\boldsymbol{\lambda}}
\newcommand{\bxi}{\boldsymbol{\xi}}
\newcommand{\vmax}{{v_\mathrm{max}}}
\newcommand{\kapint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
#1
\dd\varphi
}
\newcommand{\lamint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\lambda_{2i}}^{\frac{1}{2}\lambda_{2i+1}}
#1
\dd\varphi
}
\newcommand{\coshalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \cos\left(\frac{\bkappa}{2}\right)
}{
    \cos^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\sinhalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \sin\left(\frac{\bkappa}{2}\right)
}{
    \sin^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\DE}{\Delta \boldsymbol{E}(k^2, \bkappa)}
\newcommand{\DF}{\Delta \boldsymbol{F}(k^2, \bkappa)}
\newcommand{\sgn}{{\mathrm{sgn}}}
\newcommand{\xhat}{\ensuremath{\mathbf{\hat{x}}}\xspace}
\newcommand{\yhat}{\ensuremath{\mathbf{\hat{y}}}\xspace}
\newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}\xspace}

@@

\pagebreak

%
\section{The Problem}
\label{sec:the-problem}
%
As in \citet{Luger2019}, we compute the instantaneous visible flux $f$ from
a spherical body whose surface intensity is described by the spherical harmonic
coefficient vector $\mathbf{y}$ in some static frame $\mathcal{F}$ as
%
\begin{align}
    \label{eq:sTARRy}
    f = \bvec{s}^\top \bvec{A} \bvec{R}' \bvec{R} \bvec{y}
    \quad,
\end{align}
%
where $\bvec{R}$ and $\bvec{R}'$ are spherical harmonic rotation matrices
\citep[\S3.3 of][]{Luger2019},
$\bvec{A}$ is the change-of-basis matrix from spherical harmonics
to a basis $\tilde{\bvec{g}}$ \citep[Equation B13 in][]{Luger2019},
and $\bvec{s}^\top$ is the \emph{solution vector}, the integral of each
of the basis functions in $\tilde{\bvec{g}}$ over
the projected visible disk of the body (which may be partially occulted by
another spherical body).
%
The basis $\tilde{\bvec{g}}$ is called the \emph{Green's basis}; its name
stems from the fact that its components have a structure that makes integration
by Green's theorem convenient. Its components were defined in
Equation~11 of \citet{Luger2019b}:
%
\begin{proof}{bg}
    \tilde{g}_{l,m} &=
    \begin{dcases}
        %
        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        %
        z(x, y)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        3x^{l-2}yz(x, y)
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{even}
        \\[1em]
        %
        z(x, y)
        \bigg(
        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
        \bigg)
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \, \mathrm{odd}
        \\[1em]
        %
        z(x, y)
        \bigg(
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
        \ - \
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
        \\
        \qquad\qquad \ - \
        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
        \bigg)
         & \qquad \mathrm{otherwise}
        \quad,
    \end{dcases}
    \label{eq:bg}
\end{proof}
%
where $x$ and $y$ are the Cartesian coordinates on the surface
of the projected
disk of the body, with $z(x, y) = \sqrt{1 - x^2 - y^2}$, and
%
\begin{align}
    \label{eq:munu}
    \mu & = l - m
    \nonumber     \\
    \nu & = l + m
    \quad.
\end{align}
%
The vector $\tilde{\bvec{g}}$ is ordered such that
the component at index $n$ is $\tilde{g}_{l,m}$, with
\begin{align}
    \label{eq:lm}
    l & = \floor*{\sqrt{n}} \nonumber \\
    m & = n - l^2 - l
    \quad.
\end{align}
Finally, the rotation matrix $\bvec{R} = \bvec{R}(i, \lambda, \theta)$
rotates the body to the correct orientation on the sky given its
inclination $i$, obliquity $\lambda$, and rotational phase $\theta$,
while $\bvec{R}'$ rotates the body on the plane
of the sky into the frame $\mathcal{F}'$ in which the integration is
actually performed, with the occultor along the $+y$-axis.
For more information on all of these terms, the reader is referred to
\citet{Luger2019}.

@@

In \citet{Luger2019}, the crux of the problem was to compute the terms in the
vector $\bvec{s}^\top$, which are surface integrals over
the region of the occulted body that is visible to
the observer (Figure 2 in that paper). Here, these integrals are significantly
more difficult, because they involve not only the intersection of the
limbs of the two bodies, but also intersections with the elliptical
day/night terminator of the occulted body. Figure~\ref{fig:cases} shows the
eight families of cases involving an occultation of an illuminated body by
a spherical occultor. Each of these cases correspond to distinct ways in
which the limb of the occultor can intersect with the limb of the occulted
body and its terminator; together, these cases encompass all possible
occultation configurations, for any illumination angle, occultor size, and
occultor position. In the next three sections, we present the solution for the
$\bvec{s}^\top$, and hence for the total visible flux, for each of these cases.

% case 0: sTr
% case 1: 0
% case 2: sTr
% case 3: sTe * I + ~sTr
% case 4: sTe * I
% case 5: sTr - sT0 * I
% case 6: (sTe + sT0) * I + ~sTr
% case 7: (sTe - sT0) * I
% case 8: sT0 * I

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/cases.pdf}
        \oscaption{cases}{%
            The eight families of cases of occultations in reflected light.
            In these figures, the night side of the occulted body is colored
            black (dark grey if occulted), and the dayside is colored blue
            (light grey if occulted). The cases in the top row involve
            configurations in which the limb of the occultor does not intersect
            with the terminator at any point, so the visible flux may be
            computed in terms of classical \starry integrals. The remaining
            cases require integration along the red boundary (the curves
            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$ of
            \S\ref{sec:integration}), which
            include the terminator. These involve the evaluation of incomplete
            elliptic integrals and are derived below.
            \label{fig:cases}
        }
    \end{centering}
\end{figure}

\section{The Solution: Case 0}
\label{sec:cases-0}
%
Before we tackle configurations involving occultations, we must address the
simpler problem of computing the total visible flux from an unocculted
body in reflected light (see Figure~\ref{fig:illum}). This problem was
originally solved by \citet{Haggard2018} and subsequently adapted to the
\starry formalism in \citet{Luger2019b}, but for completeness we present
the detailed solution below.

Our task is to compute the solution vector for this
configuration, which we will denote $\bvec{s}^\top_0$.
Since in this case there is no occultor, it is
more convenient to perform the integration in a frame $\mathcal{F}''$ where the
semi-major axis of the terminator is aligned with the $x$-axis
(see Figure~\ref{fig:illum}); let us denote the matrix that rotates us
from $\mathcal{F}'$ to $\mathcal{F}''$ as $\bvec{R}''$.
It is also far easier to perform the integration
in the \emph{polynomial basis} $\tilde{\bvec{p}}$
\citep[Equation 7 in][]{Luger2019}:
%
\begin{align}
    \tilde{p}_{l,m}(x, y) & =
    \begin{dcases}
        x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
         & \qquad \mathrm{otherwise} \quad,
    \end{dcases}
\end{align}
%
where $\tilde{\bvec{p}}$ is again ordered such that the component at
index $n$ is $\tilde{p}_{l,m}$, with $l$ and $m$ given by
Equation~(\ref{eq:lm}).
Now, if $\bvec{r}^\top$ is the solution to the surface integrals in the
polynomial basis in $\mathcal{F}''$,
we may compute the desired solution vector in the Green's basis from
%
\begin{align}
    \label{eq:sTref}
    \bvec{s}^\top_0 & = \bvec{r}^\top \bvec{A_1} \bvec{R}'' \bvec{A}^{-1}
    \quad,
\end{align}
%
where $\bvec{A_1}$ \citep[Equation B11 in][]{Luger2019}
transforms the solution into the spherical harmonic basis so it can
be rotated out of the integration frame $\mathcal{F}''$ via $\bvec{R}''$, and
$\bvec{A}^{-1}$ \citep[Equation B13 in][]{Luger2019} transforms the
result into the Green's basis (in which $\bvec{s}^\top$ is defined).

Our task is thus to compute $\bvec{r}^\top$.

@@

\begin{proof}{illum}

@@

\begin{proof}{rT}

@@

    \begin{proof}{rT}
        I_{0}(b) &= \frac{\arccos(b) - bb_c}{2}

@@

        I_{1}(b) &= \frac{b_c^3}{3}

@@

    \begin{proof}{rT}
        J_{0,0} &= \pi

@@

        J_{0,1} &= \frac{4}{3}

@@

\section{The Solution: Cases 1--4}
\label{sec:cases-1-4}
Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore significantly easier to
solve.

\section{The Solution: Cases 5--8}
\label{sec:cases-5-8}
Cases 5--8 (see Figure~\ref{fig:cases}).

As in \citet{Luger2019}, the elements of the solution vector $\mathbf{s}^\top$
are given by the line integral
%
\begin{align}
    \label{eq:s}
    s_{n(\mu,\nu)} = \oint \mathbf{G}_{\mu,\nu} \cdot \dd\mathbf{r}
\end{align}
%
where
%
\begin{align}
    \label{eq:G}
    \bvec{G}_{\mu,\nu} (x, y) & =
    \begin{dcases}
        %
        x^{\frac{\mu + 2}{2}}
        y^{\frac{\nu}{2}}
        \,\yhat
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        %
        \frac{1-z(x, y)^3}{3(1-z(x, y)^2)}\bigg(-y \, \xhat + x \, \yhat\bigg)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        x^{l-2}
        z(x, y)^3
        \,\xhat
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{even}
        \\[1em]
        %
        x^{l-3}
        y
        z(x, y)^3
        \,\xhat
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{odd}
        \\[1em]
        %
        x^{\frac{\mu-3}{2}}
        y^{\frac{\nu-1}{2}}
        z(x, y)^3
        \,\yhat
         & \qquad \mathrm{otherwise,}
    \end{dcases}
\end{align}
%
and
%
\begin{align}
    \dd \bvec{r} & = -r \sin\varphi \, \dd \varphi \, \xhat +
    r \cos\varphi \, \dd \varphi \, \yhat
    \quad,
\end{align}
%
where $\varphi = \varphi(x, y)$ is the parametrized angle along the
arc of integration. Generally, there are at most three arcs bounding a given
closed surface of integration, which we will denote $\mathcal{P}$,
$\mathcal{Q}$, and $\mathcal{T}$. These are shown for a typical occultor-occulted
configuration in Figure~\ref{fig:geometry}.

\section{Performance}
\label{sec:performance}

%
\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/speed.pdf}
        \oscaption{speed}{%
            Evaluation time for the starry algorithm.
            \label{fig:speed}
        }
    \end{centering}
\end{figure}

\section{Integration}
\label{sec:integration}

\subsection{Definitions}
%
Define the pairwise difference operator
%
\begin{align}
    \label{eq:pairdiff}
    \Delta \boldsymbol{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
    \left( v_{2i + 1} - v_{2i} \right)
\end{align}
%
which sums the difference of successive pairs of values in
an array $\boldsymbol{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_N\}$.

Define the quantity
%
\begin{align}
    \label{eq:q}
    \boldsymbol{q}(k^2, \bkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
    \quad.
\end{align}

@@

\begin{proof}{T2}
    \mathcal{T}_{2}(b, \bxi) &= -\sgn(b) \Delta \boldsymbol{f}(b, \bxi)
\end{proof}
%
where
%
\begin{proof}{T2}
    \begin{split}
        f_i(b, \xi_i) =
        \frac{1}{3}\scalebox{1.4}{\Bigg(}
        &\arctan\left( \frac{|b|\sin\xi_i}{\cos\xi_i} \right)
        %
        \\
        %
        &- \sgn\left({\sin\xi_i}\right)
        \left(
        \arctan
        \left(
            \frac{
                \left(\frac{\sin\xi_i}{1 + \cos\xi_i}\right)^2 + 2 b^2 - 1
            }{2 |b| \sqrt{1 - b^2}}
            \right)
        + |b| \sqrt{1 - b^2} \cos\xi_i
        \right)
        %
        \\
        %
        &+ \phi(b, \xi_i)
        \scalebox{1.4}{\Bigg)}
    \end{split}
\end{proof}
%
and
%
\begin{proof}{T2}
    \phi(b, \xi_i) & =
    \begin{cases}
        0                          & \qquad 0 \leq \xi_i < \frac{\pi}{2}     \\
        \pi                        & \qquad \frac{\pi}{2} \leq \xi_i < \pi   \\
        2 |b| \sqrt{1 - b^2}       & \qquad \pi < \xi_i \leq \frac{3\pi}{2}  \\
        \pi + 2 |b| \sqrt{1 - b^2} & \qquad \frac{3\pi}{2} \leq \xi_i < 2\pi
        \quad.
    \end{cases}
\end{proof}

@@

\subsection{$\mathcal{W}_n$}
%
The function $\mathcal{W}_n$ is given by
%
\begin{align}
    \label{eq:W}
    % TODO
    \mathcal{W}_n = \int
\end{align}
%
This integral has a closed-form solution:
%
\begin{align}
    \label{eq:Wsol}
    \mathcal{W}_n =
    \frac{\sin^{2n + 2}\left(\frac{\bkappa}{2}\right)}{2n + 5}
    \left(
    \frac{3}{n+1}
        {_2F_1}\left(-\frac{1}{2}, n + 1; n + 2; 1 - q^2\right) + 2 q^3
    \right)
\end{align}
%
where ${_2F_1}(a, b; c; z)$ is the Gauss hypergeometric function.

>>>>

% Shorthand for this paper
\usepackage{xifthen}
\newcommand{\BF}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\BS}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\STARRYQUADPOINTS}{100\xspace}
\newcommand{\bkappa}{\BS{\kappa}}
\newcommand{\blambda}{\BS{\lambda}}
\newcommand{\bxi}{\BS{\xi}}
\newcommand{\vmax}{{v_\mathrm{max}}}
\newcommand{\kapint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
#1
\dd\varphi
}
\newcommand{\lamint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\lambda_{2i}}^{\frac{1}{2}\lambda_{2i+1}}
#1
\dd\varphi
}
\newcommand{\coshalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \cos\left(\frac{\bkappa}{2}\right)
}{
    \cos^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\sinhalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \sin\left(\frac{\bkappa}{2}\right)
}{
    \sin^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\DE}{\Delta \BS{E}(k^2, \bkappa)}
\newcommand{\DF}{\Delta \BS{F}(k^2, \bkappa)}
\newcommand{\sgn}{{\mathrm{sgn}}}
\newcommand{\xhat}{\ensuremath{\mathbf{\hat{x}}}\xspace}
\newcommand{\yhat}{\ensuremath{\mathbf{\hat{y}}}\xspace}
\newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}\xspace}
\newcommand{\sT}{\ensuremath{\BF{s}^\top}}
\newcommand{\bg}{\ensuremath{\tilde{\BF{g}}}}
\newcommand{\bp}{\ensuremath{\tilde{\BF{p}}}}

@@

%
\section{The Problem}
\label{sec:the-problem}
%
\subsection{Overview}
\label{sec:overview}
%
Without loss of generality, assume the body whose flux we wish to compute
has radius unity and sits at the origin of a right-handed Cartesian coordinate
system with the $x$-axis pointing to the right on the sky, the $y$-axis
pointing up on the sky, and the $z$-axis pointing out of the sky
toward the observer; denote this frame by $\mathcal{F}_0$. In $\mathcal{F}_0$,
the surface intensity field of the body is described by the spherical harmonic
coefficient vector $\mathbf{y}$. Following \citet{Luger2019}, we may compute
the total visible flux $f$ from this body as
%
\begin{align}
    \label{eq:sTARRy}
    f = \sT \BF{A} \BF{R}' \BF{R} \BF{y}
    \quad,
\end{align}
%
where, from right to left, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
is a Wigner rotation matrix that
rotates $\bvec{y}$ to the sky frame $\mathcal{F}_\mathrm{sky}$
given the body's inclination $i$, obliquity $\lambda$, and
rotational phase $\vartheta$,
%
$\BF{R}'$ rotates the body on the plane
of the sky into the frame $\mathcal{F}_\mathrm{int}$ in which the
integration is actually performed,
%
$\BF{A}$ is the change-of-basis matrix from spherical harmonics
to the basis in which the integrals are computed
%,
and $\sT$ is the \emph{solution vector}, the integral of each
of the basis functions over
the projected visible disk of the body (which may be partially occulted by
another spherical body). For more details, see Appendix~\ref{app:starry}.

@@

In \citet{Luger2019}, the crux of the problem was to compute the terms in the
vector $\sT$, which are surface integrals over
the region of the occulted body that is visible to
the observer (Figure 2 in that paper). Here, these integrals are significantly
more difficult, because they involve not only the intersection of the
limbs of the two bodies, but also intersections with the elliptical
day/night terminator of the occulted body.

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/cases.pdf}
        \oscaption{cases}{%
            The eight families of cases of occultations in reflected light.
            In these figures, the body with the solid outline
            is the one whose flux we are interested in, and the body with the
            dashed outline is the occultor.
            The night side of the occulted body is colored
            black (dark grey if occulted), and the dayside is colored blue
            (light grey if occulted).
            The cases in the top row involve
            configurations in which the limb of the occultor does not intersect
            with the terminator at any point, so the visible flux may be
            computed in terms of classical \starry integrals. The remaining
            cases require integration along the red boundary (the curves
            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$ of
            \S\ref{sec:cases-5-8}), which
            include the terminator. These involve the evaluation of incomplete
            elliptic integrals and are derived below.
            \label{fig:cases}
        }
    \end{centering}
\end{figure}

\subsection{Problem Setup}
\label{sec:setup}
%

Figure~\ref{fig:cases} shows the
eight families of cases involving an occultation of an illuminated body by
a spherical occultor. Each of these cases correspond to distinct ways in
which the limb of the occultor can intersect with the limb of the occulted
body and its terminator; together, these cases encompass all possible
occultation configurations, for any illumination angle, occultor size, and
occultor position. In the next three sections, we present the solution for the
$\sT$, and hence for the total visible flux, for each of these cases.

\section{The Solution}
\label{sec:solution}
%
\subsection{Case 0}
\label{sec:case-0}
%
Before we tackle configurations involving occultations, we must address the
simpler problem of computing the total visible flux from an unocculted
body in reflected light (see Figure~\ref{fig:illum}). This problem was
originally solved by \citet{Haggard2018} and subsequently adapted to the
\starry formalism in \citet{Luger2019b}, but for completeness we present
the detailed solution in Appendix~\ref{app:case0}. We will refer to the
solution vector for this case as $\sT_0$ (Equation~\ref{eq:sT0}).

\subsection{Cases 1--4}
\label{sec:cases-1-4}
%
Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore fairly
straightforward to solve.
%
Case 1 corresponds to any complete occultation of the body, so its
solution vector is trivial:
%
\begin{align}
    \label{eq:sT1}
    \sT_1 = \BS{0}
    \quad.
\end{align}
%
Case 2 involves any occultation in which the occultor blocks \emph{only} the
night side of the body (regardless of whether or not it intersects with the
limb of the body). Since the night side intensity is zero everywhere, this case
is also trivial, as the integration is the same as in case 0:
%
\begin{align}
    \label{eq:sT2}
    \sT_2 = \sT_0(b, \theta)
    \quad.
\end{align}
%
Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
the night side of the body and \emph{some} of the day side. In this
configuration, the unocculted part of the disk consists only of dayside.
Since we have no intersections with the terminator to worry about,
we may compute the total flux using the \starry formalism from
\citet{Luger2019}, provided we weight the intensity map by the illumination
field:
%
\begin{align}
    \label{eq:sT3}
    \sT_3 = \sT_\star(b_o, r_o) \BS{\Psi}(b, \theta, d_s)
    \quad,
\end{align}
%
where $\sT_\star$ is the usual \starry solution vector
\citep[Equation~26 in][]{Luger2019} and $\BS{\Psi}$ is an illumination
matrix (Appendix~\ref{app:case3}).
%
Finally, case 4 involves any occultation in which the occultor blocks
\emph{only} the day side of the body (regardless of whether or not it
intersects with the limb).
%
\begin{align}
    \label{eq:sT4}
    \sT_4 = \sT_\star(b_o, r_o) + \sT_0(-b, \theta + \pi)
    \quad.
\end{align}
%

% case 1: 0
% case 2: s0
% case 3: sTe * I
% case 4: sTe * I + ~sT0

\subsection{Cases 5--8}
\label{sec:cases-5-8}
%
Cases 5--8 (see Figure~\ref{fig:cases}, Figure~\ref{fig:geometry}).

% case 5: sT0 - sT0 * I
% case 6: (sTe + sT0) * I + ~sT0
% case 7: (sTe - sT0) * I
% case 8: sT0 * I

\section{Performance}
\label{sec:performance}
%
See Figure~\ref{fig:speed}.
%
\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/speed.pdf}
        \oscaption{speed}{%
            Evaluation time for the starry algorithm.
            \label{fig:speed}
        }
    \end{centering}
\end{figure}

\appendix

\section{The \starry formalism}
\label{app:starry}
%
The basis $\bg$ is called the \emph{Green's basis}; its name
stems from the fact that its components have a structure that makes integration
by Green's theorem convenient. Its components were defined in
Equation~11 of \citet{Luger2019b}:
%
\begin{proof}{bg}
    \tilde{g}_{l,m} &=
    \begin{dcases}
        %
        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        %
        z(x, y)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        3x^{l-2}yz(x, y)
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{even}
        \\[1em]
        %
        z(x, y)
        \bigg(
        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
        \bigg)
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \, \mathrm{odd}
        \\[1em]
        %
        z(x, y)
        \bigg(
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
        \ - \
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
        \\
        \qquad\qquad \ - \
        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
        \bigg)
         & \qquad \mathrm{otherwise}
        \quad,
    \end{dcases}
    \label{eq:bg}
\end{proof}
%
where $x$ and $y$ are the Cartesian coordinates on the surface
of the projected
disk of the body, with $z(x, y) = \sqrt{1 - x^2 - y^2}$, and
%
\begin{align}
    \label{eq:munu}
    \mu & = l - m
    \nonumber     \\
    \nu & = l + m
    \quad.
\end{align}
%
The vector $\bg$ is ordered such that
the component at index $n$ is $\tilde{g}_{l,m}$, with
%
\begin{align}
    \label{eq:lm}
    l & = \floor*{\sqrt{n}} \nonumber \\
    m & = n - l^2 - l
    \quad.
\end{align}
%
Finally, the rotation matrix $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
rotates the body to the correct orientation on the sky given its
inclination $i$, obliquity $\lambda$, and rotational phase $\vartheta$,
while $\BF{R}'$ rotates the body on the plane
of the sky into the frame $\mathcal{F}'$ in which the integration is
actually performed, with the occultor along the $+y$-axis.
For more information on all of these terms, the reader is referred to
\citet{Luger2019}.

\section{Case 0}
\label{app:case0}
%
Our task is to compute the solution vector for this
configuration, which we will denote $\BF{s}^\top_0$.
Since in this case there is no occultor, it is
more convenient to perform the integration in a frame $\mathcal{F}''$ where the
semi-major axis of the terminator is aligned with the $x$-axis
(see Figure~\ref{fig:illum}); let us denote the matrix that rotates us
from $\mathcal{F}'$ to $\mathcal{F}''$ as $\BF{R}''$.
It is also far easier to perform the integration
in the \emph{polynomial basis} $\bp$
\citep[Equation 7 in][]{Luger2019}:
%
\begin{align}
    \tilde{p}_{l,m}(x, y) & =
    \begin{dcases}
        x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
         & \qquad \mathrm{otherwise} \quad,
    \end{dcases}
\end{align}
%
where $\bp$ is again ordered such that the component at
index $n$ is $\tilde{p}_{l,m}$, with $l$ and $m$ given by
Equation~(\ref{eq:lm}).
Now, if $\BF{r}^\top$ is the solution to the surface integrals in the
polynomial basis in $\mathcal{F}''$,
we may compute the desired solution vector in the Green's basis from
%
\begin{align}
    \label{eq:sT0}
    \BF{s}^\top_0 & = \BF{r}^\top \BF{A_1} \BF{R}'' \BF{A}^{-1}
    \quad,
\end{align}
%
where $\BF{A_1}$ \citep[Equation B11 in][]{Luger2019}
transforms the solution into the spherical harmonic basis so it can
be rotated out of the integration frame $\mathcal{F}''$ via $\BF{R}''$, and
$\BF{A}^{-1}$ \citep[Equation B13 in][]{Luger2019} transforms the
result into the Green's basis (in which $\sT$ is defined).

Our task is thus to compute $\BF{r}^\top$.

@@

\begin{proof}{}

@@

\begin{proof}{}

@@

        I_{0}(b) & = \frac{\arccos(b) - bb_c}{2}

@@

        I_{1}(b) & = \frac{b_c^3}{3}

@@

        J_{0,0} & = \pi

@@

        J_{0,1} & = \frac{4}{3}

@@

\section{Case 3}
\label{app:case3}
Hello.

\section{Case 4}
\label{app:case4}
Hello.

\section{Cases 5--8}
\label{app:cases-5-8}
Hello.

As in \citet{Luger2019}, the elements of the solution vector $\mathbf{s}^\top$
are given by the line integral
%
\begin{align}
    \label{eq:s}
    s_{n(\mu,\nu)} = \oint \mathbf{G}_{\mu,\nu} \cdot \dd\mathbf{r}
\end{align}
%
where
%
\begin{align}
    \label{eq:G}
    \BF{G}_{\mu,\nu} (x, y) & =
    \begin{dcases}
        %
        x^{\frac{\mu + 2}{2}}
        y^{\frac{\nu}{2}}
        \,\yhat
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        %
        \frac{1-z(x, y)^3}{3(1-z(x, y)^2)}\bigg(-y \, \xhat + x \, \yhat\bigg)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        x^{l-2}
        z(x, y)^3
        \,\xhat
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{even}
        \\[1em]
        %
        x^{l-3}
        y
        z(x, y)^3
        \,\xhat
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{odd}
        \\[1em]
        %
        x^{\frac{\mu-3}{2}}
        y^{\frac{\nu-1}{2}}
        z(x, y)^3
        \,\yhat
         & \qquad \mathrm{otherwise,}
    \end{dcases}
\end{align}
%
and
%
\begin{align}
    \dd \BF{r} & = -r \sin\varphi \, \dd \varphi \, \xhat +
    r \cos\varphi \, \dd \varphi \, \yhat
    \quad,
\end{align}
%
where $\varphi = \varphi(x, y)$ is the parametrized angle along the
arc of integration. Generally, there are at most three arcs bounding a given
closed surface of integration, which we will denote $\mathcal{P}$,
$\mathcal{Q}$, and $\mathcal{T}$. These are shown for a typical
occultor-occulted configuration in Figure~\ref{fig:geometry}.

\subsection{Definitions}
%
Define the pairwise difference operator
%
\begin{align}
    \label{eq:pairdiff}
    \Delta \BS{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
    \left( v_{2i + 1} - v_{2i} \right)
\end{align}
%
which sums the difference of successive pairs of values in
an array $\BS{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_N\}$.

Define the quantity
%
\begin{align}
    \label{eq:q}
    \BS{q}(k^2, \bkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
    \quad.
\end{align}

@@

\begin{proof}{}
    \mathcal{T}_{2}(b, \bxi) &= -\sgn(b) \Delta \BS{f}(b, \bxi)
\end{proof}
%
where
%
\begin{proof}{}
    \begin{split}
        f_i(b, \xi_i) =
        \frac{1}{3}\scalebox{1.4}{\Bigg(}
        &\arctan\left( \frac{|b|\sin\xi_i}{\cos\xi_i} \right)
        %
        \\
        %
        &- \sgn\left({\sin\xi_i}\right)
        \left(
        \arctan
        \left(
            \frac{
                \left(\frac{\sin\xi_i}{1 + \cos\xi_i}\right)^2 + 2 b^2 - 1
            }{2 |b| \sqrt{1 - b^2}}
            \right)
        + |b| \sqrt{1 - b^2} \cos\xi_i
        \right)
        %
        \\
        %
        &+ \phi(b, \xi_i)
        \scalebox{1.4}{\Bigg)}
    \end{split}
\end{proof}
%
and
%
\begin{proof}{}
    \phi(b, \xi_i) & =
    \begin{cases}
        0                          & \qquad 0 \leq \xi_i < \frac{\pi}{2}     \\
        \pi                        & \qquad \frac{\pi}{2} \leq \xi_i < \pi   \\
        2 |b| \sqrt{1 - b^2}       & \qquad \pi < \xi_i \leq \frac{3\pi}{2}  \\
        \pi + 2 |b| \sqrt{1 - b^2} & \qquad \frac{3\pi}{2} \leq \xi_i < 2\pi
        \quad.
    \end{cases}
\end{proof}

@@

\subsection{$\mathcal{W}_n$}
%
The function $\mathcal{W}_n$ is given by
%
\begin{align}
    \label{eq:W}
    % TODO
    \mathcal{W}_n = \int
\end{align}
%
This integral has a closed-form solution:
%
\begin{proof}{}
    \label{eq:Wsol}
    \mathcal{W}_n =
    \frac{\sin^{2n + 2}\left(\frac{\bkappa}{2}\right)}{2n + 5}
    \left(
    \frac{3}{n+1}
        {_2F_1}\left(-\frac{1}{2}, n + 1; n + 2; 1 - q^2\right) + 2 q^3
    \right)
\end{proof}
%
where ${_2F_1}(a, b; c; z)$ is the Gauss hypergeometric function.
